---
title: "Reddit Politics"
output: html_document
---

```{r}
library(ggplot2)
library(RColorBrewer)
library(wordcloud)
library(tm)
library(lubridate)
library(dplyr)
library(shiny)
```


Read data from five files, merge them, and get a summary
```{r}
setwd("C:/Users/Amita/Desktop/Amita/Harvard/Semester 1/Projects/BST 260/planb/data/posts")
require(data.table)
cons_data <- as.data.frame(fread("Conservative.tsv"))
dem_data <- as.data.frame(fread("Democrats.tsv"))
lib_data <- as.data.frame(fread("Liberal.tsv"))
pol_data <- as.data.frame(fread("Politics.tsv"))
don_data <- as.data.frame(fread("The_Donald.tsv"))
#post_data <- bind_rows(cons_data, dem_data,lib_data, pol_data, don_data)
#write.csv(post_data,"C:/Users/Amita/Desktop/Amita/Harvard/Semester 1/Projects/BST 260/planb/data/posts/posts.csv")
#summary(post_data)
```


```{r}
setwd("C:/Users/Amita/Desktop/Amita/Harvard/Semester 1/Projects/BST 260/planb/data/posts")
require(data.table)
post_data <- as.data.frame(fread("posts.csv"))
summary(post_data)
```

Convert dates to standard format and extract day, month, and year.
```{r}
 as_datetime(post_data$created_utc)
post_data$day <- day(post_data$date_created)
post_data$month <- month(post_data$date_created)
post_data$year <- year(post_data$date_created)
post_data$monthyear <- paste(post_data$year,post_data$month)
```


Plot posts
```{r}
post_data$date <- as.Date(post_data$date_created)
times <- post_data %>% 
  group_by(subreddit,date) %>%
  summarise(total=n()) 
times %>%
  ggplot() +
  geom_smooth(aes(x=date,y=total,color=subreddit)) +
  scale_y_log10() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Log scaled number of posts") +
  xlab("Time") +
  ggtitle("Number of posts in subreddits over time")
```

Plot subscribers
```{r}
subs <- post_data %>% 
  na.omit(cols=subreddit_subscribers) %>%
  group_by(subreddit,date) %>%
  summarise(s=max(subreddit_subscribers,na.rm=TRUE))
subs %>%
  ggplot() +
  geom_smooth(aes(x=date,y=s,color=subreddit)) +
  scale_y_log10() +
  ylab("Log scaled number of subscribers") +
  xlab("Time") +
  ggtitle("Number of subscribers in subreddits over time")
```
Boxplot
```{r}
scores<- post_data %>%
  group_by(subreddit)
scores %>%
  ggplot() +
  geom_boxplot(aes(x=subreddit,y=score,fill=subreddit),outlier.shape = NA) +
  ylim(0, 70) +
  xlab("Subreddits") +
  ylab("Score") +
  ggtitle("Score Distributions in Subreddits")
```

Create corpus for word clouds and clean it
```{r}
cleaning<- function(data){
  docs <- Corpus(VectorSource(tolower(data$title)))
  docs<- docs %>%
  tm_map(removePunctuation) %>%
  tm_map(removeWords, stopwords("english"))
  return(docs)
}
```

Get word counts
```{r}
word_counts <- function(docs)
{
  dtm <- TermDocumentMatrix(docs)
  dtm <- removeSparseTerms(dtm, 0.99)
  matrix <- as.matrix(dtm)
  words <- sort(rowSums(matrix),decreasing=TRUE)
  word_count <- data.frame(word = names(words),freq=words)
  return(word_count)
}
```

Create word clouds
```{r}
word_clouds <- function(word_count){
  set.seed(1234)
  wc <- wordcloud(words = word_count$word, freq = word_count$freq, min.freq = 1, max.words=200, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))
  return(wc)
}
```

Form word clouds out of 5 subreddits 
```{r}
show(word_clouds(word_counts(cleaning(cons_data))))
show(word_clouds(word_counts(cleaning(dem_data))))
show(word_clouds(word_counts(cleaning(lib_data))))
show(word_clouds(word_counts(cleaning(pol_data))))
show(word_clouds(word_counts(cleaning(don_data))))
```
Polarisation
# ```{r}
# users <- post_data %>%
#   filter(author != "[deleted]") %>%
#   group_by(author,subreddit) %>%
#   summarise(total = n()) 
# users %>%
#   ggplot(aes(x=subreddit,y=subreddit))
#```

<!-- Links in subreddits -->
<!-- ```{r} -->
<!-- domain <- function(x) {strsplit(gsub("http://|https://|www\\.", "", x), "/")[[c(1, 1)]]} -->
<!-- doms <- t(as.data.frame(lapply(post_data$url,domain))) -->
<!-- post_data <- cbind(post_data,doms) -->

<!-- links <- post_data %>% dplyr::filter(domain != "reddit.com") %>% -->
<!--   group_by(subreddit,domain) %>% -->
<!--   summarise(n()) -->
<!-- ``` -->


Load comments and sentiment data
```{r}
setwd("C:/Users/Amita/Desktop/Amita/Harvard/Semester 1/Projects/BST 260/planb/data/comments")
comments <- as.data.frame(fread("comments-reduced.tsv"))
pos <- as.data.frame(fread("positive-comments.tsv"))
neg <- as.data.frame(fread("negative-comments.tsv"))
```

Handle dates and times in comments
```{r}
comments$date_created <- as_datetime(comments$created)
comments$day <- day(comments$date_created)
comments$month <- month(comments$date_created)
comments$year <- year(comments$date_created)
comments$monthyear <- paste(comments$year,post_data$month)
```

Number of comments over time mentioning different candidates
```{r}
comments$date <- as.Date(comments$date_created)
for(i in c("Conservative","democrats","Liberal","politics","The_Donald")){
  times <- comments %>% 
    filter(subreddit==i) %>%
    group_by(candidate,date) %>%
    summarise(total=n()) 
  p <- times %>%
    ggplot() +
    geom_smooth(aes(x=date,y=total,color=candidate)) +
    scale_y_log10() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
    xlab("Time") +
    ylab("Number of comments mentioning candidate") +
    ggtitle(i)
  show(p)
}

```

Load aggregate sentiment data
```{r}
setwd("C:/Users/Amita/Desktop/Amita/Harvard/Semester 1/Projects/BST 260/planb/data/comments")
agg <- as.data.frame(fread("comments-agg-sentiment.tsv"))
tw <- as.data.frame(fread("comments-timewise-sentiment.tsv"))
```


Sentiment score grouping 
```{r}
library(reshape2)
for(i in c("Conservative","democrats","Liberal","politics","The_Donald")){
  sents <- agg %>%
    filter(subreddit==i) %>%
    group_by(candidate) %>%
    melt(id.vars="candidate",measure.vars=c("positive","negative"))
  p<-sents %>%
    ggplot(aes(x=candidate,y=value,fill=variable)) +
    geom_bar(stat="identity",position="fill") +
    xlab("Candidate") +
    ylab("Sentiment") +
    ggtitle(i)
  show(p)
}
```

Timewise aggregate sentiments for candidates
```{r}
tw$date <- as_datetime(tw$timestamp)
for(i in c("Conservative","democrats","Liberal","politics","The_Donald")){
  times <- tw %>% 
    filter(subreddit==i) %>%
    group_by(candidate,date) 
  p <- times %>%
    ggplot() +
    geom_smooth(aes(x=date,y=score,color=candidate)) +
    scale_y_log10() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
    xlab("Time") +
    ylab("Score aggregate") +
    ggtitle(i)
  show(p)
}
```


Frequently used words in positive and negative comments
```{r}
names(pos)[names(pos) == "body"] <- "title"
names(neg)[names(neg) == "body"] <- "title"
show(word_clouds(word_counts(cleaning(pos))))
show(word_clouds(word_counts(cleaning(neg))))
```

